Checkpoint 4

### 2020-05-01 Draft-Report.Rmd
stuff

```{r}
set.seed(454)
model_1 <- stan_glm(
  ChinaVirusInterest ~ Day + percent_white+StateColor+positive,
  data = model_data, family = gaussian,
  chains = 4, iter = 1000, refresh = 0
)
model_1
```
As we can see in our summary table, we see that the higher the percent_white we see a higher median of China Virus Interest states with higher percent_white populations tend to have higher searches for "China Virus". And we also see that compared to State Color Blue state Color Red tends to have -3.2% less searches. We also see that the positive number of cases did not change the mean value for China Virus Interest which we found interesting. Basically telling us that maybe COVID-related variables do not have a big effect on how much people search for these terms.

>>>>

```{r}
set.seed(454)
model_1 <- stan_glm(
  ChinaVirusInterest ~ Day + percent_white+StateColor+positive,
  data = model_data, family = gaussian,
  chains = 4, iter = 1000, refresh = 0
)
model_1
```

As we can see in our summary table, we see that the higher the percent_white we see a higher median of China Virus Interest states with higher percent_white populations tend to have higher searches for "China Virus". And we also see that compared to State Color Blue state Color Red tends to have -3.2% less searches. We also see that the positive number of cases did not change the mean value for China Virus Interest which we found interesting. Basically telling us that maybe COVID-related variables do not have a big effect on how much people search for these terms.
